Tail Indices and Scale Parameters in Financial Time Series

### 2017-03-13 papers/FX/draft.tex
There is still some hope in the Student's t and log-utility situation.

Routledge and Zin \cite{routledge2010generalized} assumed
a power-law utility function of $C$:
\begin{equation}
  \label{eq:power_utility}
  u(C)=\frac{1}{1-\gamma}C^{1-\gamma}%  
\end{equation}
where $\gamma > 0$. For our discussion it suffices that $u(\cdot)$ is
increasing and concave. Before proceeding any further, it is worth
stating the following simple observation:
\begin{lemma} \label{lemma:I}
  Assume distribution function $F(x; \theta)$ parameterized by
  $\theta$ is defined on $x \in (a, b)$, $a, b \in \mathbb R \cup
  \{-\infty, \infty\}$, and in addition $F(x; \theta)$ has density
  function $f(x; \theta)$. Assume function $h(\cdot)$ is defined on
  $(a, b)$, $X \sim F$, $\text{supp}(X) = (a,b)$,
  $\E h(X) < \infty$ and
  \begin{eqnarray*}
    \opd{\theta}\left[
      F(b) - F(a)
    \right] = 0 \\
    \left| \pd{f(x, \theta)}{\theta} \right| < \infty
    \quad \forall x \in (a, b)
  \end{eqnarray*}
  \begin{enumerate}
  \item If $h(\cdot)$ is decreasing and $\exists x_0 \in (a, b)$ such that
    $\pd{f}{\theta}(x_0; \theta) > 0$ on $(a, x_0)$ while
    $\pd{f}{\theta}(x_0; \theta) < 0$ on $(x_0, b)$, then
    \[
    \pd{\E h(X)}{\theta} > 0
    \]
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    $\pd{f}{\theta}(x_0; \theta) < 0$ on $(a, x_0)$  while
    $\pd{f}{\theta}(x_0; \theta) > 0$ on $(x_0, b)$, then
    \[
    \pd{\E h(X)}{\theta} > 0
    \]
  \end{enumerate}
\end{lemma}
\begin{remark}
  \label{remark:I}
  Two other cases follow trivially from lemma \ref{lemma:I}:
  \begin{enumerate}
  \item If $h(\cdot)$ is increasing and $\pd{f}{\theta}$ satisfies the
    same conditions of the 1st case of lemma \ref{lemma:I},
    $\pd{\E h(X)}{\theta} < 0$. This immediately follows from applying
    1st case of lemma \ref{lemma:I} to $-h(\cdot)$.
  \item By the same argument, if $h(\cdot)$ is decreasing and
    $\pd{f}{\theta}$ satisfies the same conditions of the 2nd case of
    lemma \ref{lemma:I}, $\pd{\E h(X)}{\theta} < 0$.
  \end{enumerate}
\end{remark}
Now for simplicity we assume the investor initially has one unit of
wealth. Let $r > 0$ be the return on the risk free state bond and $X$
be the return on equity. Portfolio weights are $\left(1-\phi\right)$
and $\phi$ respectively. Then
\begin{equation}
  \label{eq:xxie1}
  C = (1 - \phi) e^r + \phi e^X
\end{equation}
Equation \eqref{eq:xxie0} can be re-arranged as
\begin{eqnarray}
u(v) &=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) \P[C < \delta v] \nonumber \\
&=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q) \label{eq:functional}
\end{eqnarray}
where
\begin{eqnarray*}
  q = q(r, \phi) &:=& \ln \left( {
      \delta v - (1 - \phi) e^r
      \over
      \phi
    } \right) = \ln\left(
    e^r + {\delta v - e^r \over \phi}
  \right)
\end{eqnarray*}
Note $C < \delta v$ implies $X < q$. Naturally, if an agent invests in
a risky asset instead of a riskless bond, he expects to obtain a
higher return from the risky asset than he is guarranteed from the
riskless bond. In our notation, this means $\delta v > e^r$, which
implies $q(r, \phi) > r > 0$. The right-hand-side of
\eqref{eq:functional} is a functional of $\phi$ and the distribution
function of $X$ via \eqref{eq:xxie1}. For convenience we denote it
$\mathcal U(\cdot, \cdot)$, i.e.
\begin{equation}
  \label{eq:U_functional}
  \mathcal U(F, \phi)
  = 
  \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q(r, \phi))
\end{equation}
In the rest of this section, we use $F(\cdot)$ to denote the
distribution function of $X$ and use $f(\cdot)$ to denote its density
function. Let
\begin{equation}
  \label{eq:G_functional}
  G(F) = \max_{0 < \phi \leq 1} \mathcal U(F, \phi)  
\end{equation}

@@

\subsubsection{log-utility function}
We first consider the case where the utility function is simply
$u(\cdot) = \ln(\cdot)$. This corresponds to the limiting case of
\eqref{eq:power_utility} as $\gamma \to 0$.
\begin{theorem}
  Suppose functional $G(\cdot)$ is given as \eqref{eq:G_functional},
  function $u(\cdot) = \ln(\cdot)$, then
  \[
  \pd{G(F)}{\nu} < 0
  \]
  where $F(x, \nu)$ is the Student's t-distribution function.
\end{theorem}
\begin{proof}
  By the same argument as in the proof of theorem \ref{thrm:I}, it
  suffices to show
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\nu}(\nu, \hat\phi) &<& 0
  \end{eqnarray*}
  where $\hat\phi$ is defined in \eqref{eq:xxie2}. We have
  \begin{eqnarray*}
    && \mathcal U(F, \phi) \\
    &=&
    \int_{-\infty}^\infty
    u[(1 - \phi) e^r + \phi e^x] (1 + b \1{x < q}) f(x, \nu) dx
  \end{eqnarray*}

\end{proof}

Then it follows
\begin{eqnarray}
\pd{f(x, \nu)}{\nu} &=& {
  c(\nu) x^2 (\nu + 1) + (2 \nu x^2 + 2 \nu^2) c'(\nu)
  -
  \nu c(\nu) (x^2 + \nu) \ln(1 + x^2/\nu)
  \over
  2 \nu (x^2 + \nu) (1 + x^2 / \nu)^{\nu/2 + 1/2}
  } \nonumber \\
  &:=& {
    P(x^2, \nu)
    \over
    2 \nu (x^2 + \nu) (1 + x^2 / \nu)^{\nu/2 + 1/2}
  }
  \label{eq:xxie4.1}
\end{eqnarray}

While the denominator of the right side of $\pd{f(x, \nu)}{\nu}$ is
always positive, its nummerator $P(x^2, \nu)$ has a single root:
\begin{equation}
  \label{eq:xxie5}
  x_0^2 = \nu\exp\left\{
    W\left[
      -\left(1 + {1 \over \nu}\right)
      e^{-1 - 2 c'(\nu)/c(\nu) - 1/\nu}
    \right]
    + 1 + {1 \over \nu} + {2 c'(\nu) \over c(\nu)}
  \right\} - \nu
\end{equation}
where $W(\cdot)$ is the principle branch of the Lambert $W$
function. and $c'(\cdot)$ is the derivative of $c(\cdot)$. To check
the right side of \eqref{eq:xxie5} for positivity, we first note
$c'(\nu) > 0$:
\[
c'(\nu) = {
  \pi \Gamma(\nu/2 + 1/2) \left\{
    \nu \left[ \Psi(\nu/2 + 1/2) - \Psi(\nu/2)\right] - 1
  \right\}
  \over
  2 \Gamma(\nu/2) (\pi \nu)^{3/2}
}
\]
where $\Psi(\cdot)$ is the digamma function:
\[
\Psi(x) = \td{\ln[\Gamma(x)]}{x}
\]
\begin{minipage}{0.48\textwidth}
  $\Psi(x)$ \linebreak
  \includegraphics[width=\textwidth]{digamma.png}
\end{minipage}\hfill
\begin{minipage}{0.5\textwidth}
  As shown in the figure to the left, $\Psi(x)$ is increasing
  for $x > 0$. Therefore $\Psi(\nu/2 + 1/2) - \Psi(\nu/2) > 0$.
  So we have
  \begin{eqnarray*}
    && \nu \left[
    \Psi(\nu/2 + 1/2) - \Psi(\nu/2)
    \right] - 1 \\
    &\geq& 1 \times \left[
    \Psi(1/2 + 1/2) - \Psi(1/2)
    \right] - 1 \\
    &=& \ln(4) - \ln(e) \\
    &>& 0
  \end{eqnarray*}
  Thus $c'(\nu) > 0$. Furthermore, we recall
  $W(\cdot)$ is increasing on its principle branch. So
\end{minipage}
\begin{eqnarray*}
  &&
  W\left[
    -\left( 1 + {1 \over \nu} \right)
    e^{-1 - 2 c'(\nu)/c(\nu) - 1/\nu}
  \right]
  + 1 + {1 \over \nu} + {2 c'(\nu) \over c(\nu)} \\
  &>& 
  W\left[
    -\left( 1 + {1 \over \nu} + {2 c'(\nu) \over c(\nu)} \right)
    e^{-1 - 2 c'(\nu)/c(\nu) - 1/\nu}
  \right]
  + 1 + {1 \over \nu} + {2 c'(\nu) \over c(\nu)} \\
  &=& W(-y e^{-y}) + y
\end{eqnarray*}
where
\[
y = 1 + {1 \over \nu} + {2 c'(\nu) \over c(\nu)} > 1
\]
Now notice
\[
\ln(y e^{-y}) = \ln(y) - y
\]
is a decreasing function for $y > 1$. Thus $-y e^{-y}$ is an
increasing function. Hence we have
\begin{eqnarray*}
  W(-y e^{-y}) + y &>& W(-e^{-1}) + 1 = 0
\end{eqnarray*}
Now it is clear
\[
\nu\exp\left\{
    W\left[
      -\left(1 + {1 \over \nu}\right)
      e^{-1 - 2 c'(\nu)/c(\nu) - 1/\nu}
    \right]
    + 1 + {1 \over \nu} + {2 c'(\nu) \over c(\nu)}
  \right\} - \nu > 0
\]
Now that we have established that $\pd{f}{\nu}(x, \nu) = 0$ has a
single positive root, it remains to determine the sign of
$\pd{f}{\nu}(x, \nu)$ on the two sides of the root in order to apply
lemma \ref{lemma:I}. For this purpose we observe
\begin{equation}
  \label{eq:xxie5.1}
  P(0, \nu) = 2 \nu^2 c'(\nu) > 0
\end{equation}
So we want to investigate $\pd{P}{x^2}(x^2, \nu)$:
\begin{eqnarray}
  && \pd{P}{x^2}(x^2, \nu) \nonumber \\
  &=&
  2 \nu c'(\nu) + c(\nu) - \nu c(\nu) \ln\left(
  1 + {x^2 \over \nu}
  \right)
  \label{eq:xxie6}
\end{eqnarray}
From \eqref{eq:xxie5.1} and \eqref{eq:xxie6} it is clear
$P(x^2, \nu) > 0$ for $0 \leq x^2 < x_0^2$ and
$P(x^2, \nu) < 0$ for $x^2 > x_0^2$.

\section{Review of multivariate GARCH models:
  same tail index or not}
Many multivariate GARCH models imply a common tail index for all
series under consideration, e.g. the Orthogonal GARCH model of
Alexander and Chibumba (1997) \cite{alexander1997multivariate}, its
generalization GO-GARCH of van der Weide (2002) \cite{van2002go}, as
well as the Full Factor GARCH model of Vrontos et al (2003)
\cite{vrontos2003full} and the Generalized Orthogonal Factor GARCH
model of Lanne and Saikkonen (2007) \cite{lanne2007modeling}. These
models are characterized by their treatment of each series as a linear
combination of factors, and each of the factors is modeled as a GARCH
process. As a result of this treatment, each and every series under
consideration necessarily has the lowest of the tail indices of its
contributing factors (cf. Mikosch (2013) \cite{Mikosch2013} as well
as Andersen, Davis, Kreiss and Mikosch (2009)
\cite{andersen2009handbook}).

>>>>

Routledge and Zin \cite{routledge2010generalized} assumed
a power-law utility function of $C$:
\begin{equation}
  \label{eq:power_utility}
  u(C)=\frac{1}{1-\gamma}C^{1-\gamma}%  
\end{equation}
where $\gamma > 0$. For our discussion it suffices that $u(\cdot)$ is
increasing and concave. Before proceeding any further, it is worth
stating the following simple observation:
\begin{lemma} \label{lemma:I}
  Assume distribution function $F(x; \theta)$ parameterized by
  $\theta$ is defined on $x \in (a, b)$, $a, b \in \mathbb R \cup
  \{-\infty, \infty\}$, and in addition $F(x; \theta)$ has density
  function $f(x; \theta)$. Assume function $h(\cdot)$ is defined on
  $(a, b)$, $X \sim F$, $\text{supp}(X) = (a,b)$,
  $\E h(X) < \infty$ and
  \begin{eqnarray*}
    \opd{\theta}\left[
      F(b) - F(a)
    \right] = 0 \\
    \left| \pd{f(x, \theta)}{\theta} \right| < \infty
    \quad \forall x \in (a, b)
  \end{eqnarray*}
  \begin{enumerate}
  \item If $h(\cdot)$ is decreasing and $\exists x_0 \in (a, b)$ such that
    $\pd{f}{\theta}(x_0; \theta) > 0$ on $(a, x_0)$ while
    $\pd{f}{\theta}(x_0; \theta) < 0$ on $(x_0, b)$, then
    \[
    \pd{\E h(X)}{\theta} > 0
    \]
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    $\pd{f}{\theta}(x_0; \theta) < 0$ on $(a, x_0)$  while
    $\pd{f}{\theta}(x_0; \theta) > 0$ on $(x_0, b)$, then
    \[
    \pd{\E h(X)}{\theta} > 0
    \]
  \end{enumerate}
\end{lemma}
\begin{remark}
  \label{remark:I}
  Two other cases follow trivially from lemma \ref{lemma:I}:
  \begin{enumerate}
  \item If $h(\cdot)$ is increasing and $\pd{f}{\theta}$ satisfies the
    same conditions of the 1st case of lemma \ref{lemma:I},
    $\pd{\E h(X)}{\theta} < 0$. This immediately follows from applying
    1st case of lemma \ref{lemma:I} to $-h(\cdot)$.
  \item By the same argument, if $h(\cdot)$ is decreasing and
    $\pd{f}{\theta}$ satisfies the same conditions of the 2nd case of
    lemma \ref{lemma:I}, $\pd{\E h(X)}{\theta} < 0$.
  \end{enumerate}
\end{remark}
Now for simplicity we assume the investor initially has one unit of
wealth. Let $r > 0$ be the return on the risk free state bond and $X$
be the return on equity. Portfolio weights are $\left(1-\phi\right)$
and $\phi$ respectively. Then
\begin{equation}
  \label{eq:xxie1}
  C(X) = (1 - \phi) e^r + \phi e^X
\end{equation}
Equation \eqref{eq:xxie0} can be re-arranged as
\begin{eqnarray}
u(v) &=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) \P[C < \delta v] \nonumber \\
&=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q) \label{eq:functional}
\end{eqnarray}
where
\begin{eqnarray*}
  q = q(r, \phi) &:=& \ln \left( {
      \delta v - (1 - \phi) e^r
      \over
      \phi
    } \right) = \ln\left(
    e^r + {\delta v - e^r \over \phi}
  \right)
\end{eqnarray*}
Note $C < \delta v$ implies $X < q$. Naturally, if an agent invests in
a risky asset instead of a riskless bond, he expects to obtain a
higher return from the risky asset than he is guarranteed from the
riskless bond. In our notation, this means $\delta v > e^r$, which
implies $q(r, \phi) > r > 0$. The right-hand-side of
\eqref{eq:functional} is a functional of $\phi$ and of the distribution
function of $X$ via \eqref{eq:xxie1}. For convenience we denote it
$\mathcal U(\cdot, \cdot)$, i.e.
\begin{equation}
  \label{eq:U_functional}
  \mathcal U(F, \phi)
  = 
  \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q(r, \phi))
\end{equation}
In the rest of this section, we use $F(\cdot)$ to denote the
distribution function of $X$ and use $f(\cdot)$ to denote its density
function. Let
\begin{equation}
  \label{eq:G_functional}
  G(F) = \max_{0 < \phi \leq 1} \mathcal U(F, \phi)  
\end{equation}

@@

\subsubsection{log-utility function}
We first consider the case where the utility function is simply
$u(\cdot) = \ln(\cdot)$. This corresponds to the limiting case of
\eqref{eq:power_utility} as $\gamma \to 0$.
\begin{theorem}
  Suppose functional $G(\cdot)$ is given as \eqref{eq:G_functional},
  function $u(\cdot) = \ln(\cdot)$, then
  \[
  \pd{G(F)}{\nu} < 0
  \]
  where $F(x, \nu)$ is the Student's t-distribution function.
\end{theorem}
\begin{proof}
  By the same argument as in the proof of theorem \ref{thrm:I}, it
  suffices to show
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\nu}(\nu, \hat\phi) &<& 0
  \end{eqnarray*}
  where $\hat\phi$ is defined in \eqref{eq:xxie2}. We have
  \begin{eqnarray*}
    && \mathcal U(F, \phi) \\
    &=&
    \int_{-\infty}^\infty
    \ln[C(x)] (1 + b \1{x < q})f(x, \nu) dx
    - b \ln(\delta v) F(q, \nu) \\
    &=& 
    \int_{0}^\infty
    \ln\left[C(x) C(-x)\right]
    f(x, \nu) dx
    +
    b \int_{-\infty}^\infty
    \ln
    \left[
      C(x)
      \over
      C(q)
    \right]
    \1{x < q} f(x, \nu) dx \\
    &=&
    \underbrace{
      \int_{0}^\infty
      \ln\left[C(x) C(-x)\right]
      f(x, \nu) dx
    }_{I_1}
    +
    b \underbrace{
      \int_{0}^\infty
      \left\{
      \ln
      \left[
        C(x)
        \over
        C(q)
        \right]
      \1{x < q}
      +
      \ln\left[
        C(-x)
        \over
        C(q)
        \right]
      \right\}
      f(x, \nu) dx
    }_{I_2}
  \end{eqnarray*}
  where $C(\cdot)$ is defined in \eqref{eq:xxie1}.
  Observe that $\ln(C(x)C(-x))$ is an increasing function:
  \begin{eqnarray*}
    \opd{x}
    \left[
      \ln(C(x) C(-x))
    \right]
    &=&
    {
      \phi (1- \phi) e^r (e^x - e^{-x})
      \over
      ((1 - \phi) e^r + \phi e^x)
      ((1 - \phi) e^r + \phi e^{-x})
    } > 0
  \end{eqnarray*}
  Thus by 1st case of remark \ref{remark:I} and lemma \ref{lemma:II},
  $\pd{I_1}{\nu} < 0$. If $b = 0$, i.e.
  $\mathcal U(F, \phi) = \E u(C(X))$, then we have concluded
  $\pd{G(F)}{\nu} < 0$. Otherwise we need to investigate $I_2$:
  \begin{enumerate}
  \item In case $q \leq x_0$, by lemma \ref{lemma:II},
    $\pd{f}{\nu}(x, \nu) > 0$ for $x \leq q < x_0$. Moreover
    \[
    \ln\left[
      C(-x)
      \over
      C(q)
      \right] < 0
    \quad
    \forall x > 0
    \]
    Therefore
    \begin{eqnarray*}
      \pd{I_2}{\nu}
      &<&
      \int_{0}^\infty
      \ln
      \left[
        C(x) C(-x)
        \over
        C(q)^2
        \right]
      \1{x < q}
      \pd{f}{\nu}(x, \nu) dx \\
      &&
      + \int_{0}^\infty
      \ln
      \left[
        C(-x)
        \over
        C(q)
        \right]
      \1{x > x_0}
      \pd{f}{\nu}(x, \nu) dx \\
    \end{eqnarray*}

  \item If $q > x_0$
  \end{enumerate}

  \begin{eqnarray}
    \pd{f(x, \nu)}{\nu} &=& {
      c(\nu) x^2 (\nu + 1) + (2 \nu x^2 + 2 \nu^2) c'(\nu)
      -
      \nu c(\nu) (x^2 + \nu) \ln(1 + x^2/\nu)
      \over
      2 \nu (x^2 + \nu) (1 + x^2 / \nu)^{\nu/2 + 1/2}
    } \nonumber \\
    &:=& {
      P(x^2, \nu)
      \over
      2 \nu (x^2 + \nu) (1 + x^2 / \nu)^{\nu/2 + 1/2}
    }
    \label{eq:xxie4.1}
  \end{eqnarray}

  While the denominator of the right side of $\pd{f(x, \nu)}{\nu}$ is
  always positive, its nummerator $P(x^2, \nu)$ has a single root:
  \begin{equation}
    \label{eq:xxie5}
    x_0^2 = \nu\exp\left\{
    W\left[
      -\left(1 + {1 \over \nu}\right)
      e^{-1 - 2 c'(\nu)/c(\nu) - 1/\nu}
      \right]
    + 1 + {1 \over \nu} + {2 c'(\nu) \over c(\nu)}
    \right\} - \nu
  \end{equation}
  where $W(\cdot)$ is the principle branch of the Lambert $W$
  function. and $c'(\cdot)$ is the derivative of $c(\cdot)$. To check
  the right side of \eqref{eq:xxie5} for positivity, we first note
  $c'(\nu) > 0$:
  \[
  c'(\nu) = {
    \pi \Gamma(\nu/2 + 1/2) \left\{
    \nu \left[ \Psi(\nu/2 + 1/2) - \Psi(\nu/2)\right] - 1
    \right\}
    \over
    2 \Gamma(\nu/2) (\pi \nu)^{3/2}
  }
  \]
  where $\Psi(\cdot)$ is the digamma function:
  \[
  \Psi(x) = \td{\ln[\Gamma(x)]}{x}
  \]
  \begin{minipage}{0.48\textwidth}
    $\Psi(x)$ \linebreak
    \includegraphics[width=\textwidth]{digamma.png}
  \end{minipage}\hfill
  \begin{minipage}{0.5\textwidth}
    As shown in the figure to the left, $\Psi(x)$ is increasing
    for $x > 0$. Therefore $\Psi(\nu/2 + 1/2) - \Psi(\nu/2) > 0$.
    So we have
    \begin{eqnarray*}
      && \nu \left[
        \Psi(\nu/2 + 1/2) - \Psi(\nu/2)
        \right] - 1 \\
      &\geq& 1 \times \left[
        \Psi(1/2 + 1/2) - \Psi(1/2)
        \right] - 1 \\
      &=& \ln(4) - \ln(e) \\
      &>& 0
    \end{eqnarray*}
    Thus $c'(\nu) > 0$. Furthermore, we recall
    $W(\cdot)$ is increasing on its principle branch. So
  \end{minipage}
  \begin{eqnarray*}
    &&
    W\left[
      -\left( 1 + {1 \over \nu} \right)
      e^{-1 - 2 c'(\nu)/c(\nu) - 1/\nu}
      \right]
    + 1 + {1 \over \nu} + {2 c'(\nu) \over c(\nu)} \\
    &>& 
    W\left[
      -\left( 1 + {1 \over \nu} + {2 c'(\nu) \over c(\nu)} \right)
      e^{-1 - 2 c'(\nu)/c(\nu) - 1/\nu}
      \right]
    + 1 + {1 \over \nu} + {2 c'(\nu) \over c(\nu)} \\
    &=& W(-y e^{-y}) + y
  \end{eqnarray*}
%   where
%   \[
%   y = 1 + {1 \over \nu} + {2 c'(\nu) \over c(\nu)} > 1
%   \]
%   Now notice
%   \[
%   \ln(y e^{-y}) = \ln(y) - y
%   \]
%   is a decreasing function. Thus $-y e^{-y}$ is an increasing
%   function. Hence we have
%   \begin{eqnarray*}
%     W(-y e^{-y}) + y &>& W(-e^{-1}) + 1 = 0
%   \end{eqnarray*}
%   Now it is clear
%   \[
%   \nu\exp\left\{
%   W\left[
%     -\left(1 + {1 \over \nu}\right)
%     e^{-1 - 2 c'(\nu)/c(\nu) - 1/\nu}
%   \right]
%   + 1 + {1 \over \nu} + {2 c'(\nu) \over c(\nu)} \\
%   &=& W(-y e^{-y}) + y
% \end{eqnarray*}
where
\[
y = 1 + {1 \over \nu} + {2 c'(\nu) \over c(\nu)} > 1
\]
Now notice
\[
\ln(y e^{-y}) = \ln(y) - y
\]
is a decreasing function for $y > 1$. Thus $-y e^{-y}$ is an
increasing function. Hence we have
\begin{eqnarray*}
  W(-y e^{-y}) + y &>& W(-e^{-1}) + 1 = 0
\end{eqnarray*}
Now it is clear
\[
\nu\exp\left\{
    W\left[
      -\left(1 + {1 \over \nu}\right)
      e^{-1 - 2 c'(\nu)/c(\nu) - 1/\nu}
    \right]
  + 1 + {1 \over \nu} + {2 c'(\nu) \over c(\nu)}
  \right\} - \nu > 0
  \]
  Now that we have established that $\pd{f}{\nu}(x, \nu) = 0$ has a
  single positive root, it remains to determine the sign of
  $\pd{f}{\nu}(x, \nu)$ on the two sides of the root in order to apply
  lemma \ref{lemma:I}. For this purpose we observe
  \begin{equation}
    \label{eq:xxie5.1}
    P(0, \nu) = 2 \nu^2 c'(\nu) > 0
  \end{equation}
  So we want to investigate $\pd{P}{x^2}(x^2, \nu)$:
  \begin{eqnarray}
    && \pd{P}{x^2}(x^2, \nu) \nonumber \\
    &=&
    2 \nu c'(\nu) + c(\nu) - \nu c(\nu) \ln\left(
    1 + {x^2 \over \nu}
    \right)
    \label{eq:xxie6}
  \end{eqnarray}
  From \eqref{eq:xxie5.1} and \eqref{eq:xxie6} it is clear
  $P(x^2, \nu) > 0$ for $0 \leq x^2 < x_0^2$ and
  $P(x^2, \nu) < 0$ for $x^2 > x_0^2$.

\end{proof}
\section{Review of multivariate GARCH models:
  same tail index or not}
Many multivariate GARCH models imply a common tail index for all
series under consideration, e.g. the Orthogonal GARCH model of
Alexander and Chibumba (1997) \cite{alexander1997multivariate}, its
generalization GO-GARCH of van der Weide (2002) \cite{van2002go}, as
well as the Full Factor GARCH model of Vrontos et al (2003)
\cite{vrontos2003full} and the Generalized Orthogonal Factor GARCH
model of Lanne and Saikkonen (2007) \cite{lanne2007modeling}. These
models are characterized by their treatment of each series as a linear
combination of factors, and each of the factors is modeled as a GARCH
process. As a result of this treatment, each and every series under
consideration necessarily has the lowest of the tail indices of its
contributing factors (cf. Mikosch (2013) \cite{Mikosch2013} as well
as Andersen, Davis, Kreiss and Mikosch (2009)
\cite{andersen2009handbook}).
